Compositional Quantitative Resource Analysis of C Programs

### 2014-06-08 paper/main.tex
finished the description of t16

\begin{figure*}[t!]
\newlength{\progwidth}
\setlength{\progwidth}{.19\linewidth}
  \centering

$4|[0,x]| + [|0,y|]$
\\[.7\baselineskip]
      {\bf t07}
    \end{center}
  \end{minipage}%
%
%
%
  \begin{minipage}[b]{\progwidth}
    \begin{center}
   \begin{lstlisting}
  while (z-y>0) {
    y = y+1;
  }
  while (y>9) {
    y=y-10;
  }
   \end{lstlisting}

@@

$12|[n,0]| + 0.1|[0,y]|$
\\[.7\baselineskip]
      {\bf t27}
    \end{center}
  \end{minipage}
%
%
%
  \begin{minipage}[b]{\progwidth}
    \begin{center}
   \begin{lstlisting}
  while (x>y) {
    x=x-1;
    x=x+1000;
    y=y+1000;
  }
  while (y>0) {
    y=y-1;
  }
  while (x<0) {
    x=x+1;
  }
   \end{lstlisting}

@@

   \caption{Amortization and Compositionality}
  \label{fig:cat1}
\end{figure*}

@@

>>>>

\newlength{\progwidth}

\begin{figure*}[t!]
\setlength{\progwidth}{.24\linewidth}
  \centering

  \begin{minipage}[b]{\progwidth}
    \begin{center}
   \begin{lstlisting}
  while (z-y>0) {
    y = y+1;
  }
  while (y>9) {
    y=y-10;
  }
   \end{lstlisting}

@@

$12|[n,0]| + 0.1|[0,y]|$
\\[.7\baselineskip]
      {\bf t27}
    \end{center}
  \end{minipage}
   \caption{Amortization and Compositionality (a)}
  \label{fig:cat1a}
\end{figure*}

\begin{figure*}[t!]
 \setlength{\progwidth}{.24\linewidth}
  \centering

$4|[0,x]| + [|0,y|]$
\\[.7\baselineskip]
      {\bf t07}
    \end{center}
  \end{minipage}%
%
%
%
  \begin{minipage}[b]{\progwidth}
    \begin{center}
   \begin{lstlisting}
  while (x>y) {
    x=x-1;
    x=x+1000;
    y=y+1000;
  }
  while (y>0) {
    y=y-1;
  }
  while (x<0) {
    x=x+1;
  }
   \end{lstlisting}

@@

   \caption{Amortization and Compositionality (b)}
  \label{fig:cat1b}
\end{figure*}

@@

Example \emph{t16} is an extension of example \emph{t15}. We again
assume that $y$ is non-negative and use the same mechanism to iterate
the outer loop as in \emph{t15}.  In the inner loop, we also count the
variable $z$ down to zero and perform $|[0,z]|$ interations.  However,
insead of assigning $z=y$, we assign $z=2y+100$.  The analysis
computes the tight linear bound $1+2|[0,x]|+103|[y,x]|$.  The
assignment of potential to the size interval $|[y,x]|$ in instead of
$|[0,x]|$ is a random choice of the LP solver.  Other optimal
solutions of the linear program that the analyzer gernerates for
\emph{t15} would result in bounds such as $1+105|[0,x]|$ or
$1+6|[0,x]|+99|[y,x]|$.  In fact, the $105$ potential units can be
shared arbitrarily between the interval sizes $|[y,x]|$ and $|[0,x]|$
as long as more than $1$ unit is assigned to $|[0,x]|$.  Since we know
that $y\geq 0$ the choice of the LP solver is optimal but this seems
to be a coincidence.
